---
title: "Creating customised DNA reference databases - Amplicon specific libraries"
author: "Jessica Chung /Melissa Carew"
date: "15/02/2024"
output: html_document
---

--------------------------------------------------------------------------------
#SECTION 5: Creating amplicon specific libraries for bioinformatic pipelines
Unfortunately, the primer cropping in refdb does not work! I could not get refdb to properly trim primers it needed really high error setting to do any trimming, but with these settings over trimmed most of the data. for the short amplicon the forward primer trims ok but the reverse trims in the wrong spot.

Therefore for this step we can use cutadapt.
# Load packages

```{r message=FALSE, warning=FALSE}
suppressPackageStartupMessages({
library(dplyr)
library(refdb)
library(bioseq)
library(here)  
library(stringr)})
```


# load library (IF NEEDED)

```{r}
all_db <- readRDS(here::here("final_library/all_bold_priv_NCBI_final_clean_Nov23.rds"))
```


#Step 1: set fields for refdb
```{r}
all_db <- refdb::refdb_set_fields(all_db,
                             taxonomy = c(kingdom = "superkingdom",
                               phylum = "phylum",
                               class = "class",
                               order = "order",
                               family = "family",
                               genus = "genus",
                               species = "species"),
                             sequence = "sequence",
                             marker = "marker",
                             source = "source",
                             id = "id")

refdb::refdb_get_fields(all_db)
```

```{r}
# check there are no duplicate ids codes
length(unique(all_db$id)) == nrow(all_db)

#if true move on
```

```{r}
# check flie size
all_db %>% object.size()
```

# check file column names (DNA_seq = sequence data)
```{r}
head (all_db)
```

#Step 2: Convert to fasta file for trimming in cutadapt
The file size is large so it can be partitioned for this step (in 4 parts here). The input files for cutadapt is .fasta
```{r}
seqs <- all_db[, "sequence",drop=TRUE]
names(seqs) <- 1:nrow(all_db)
parts <- as.numeric(cut(seq_along(seqs), 4))
bioseq::write_fasta(seqs[parts == 1], file = here::here("final_library/trimming/all_db.fasta"),
                    line_length = 80, block_length=Inf, append=FALSE)
bioseq::write_fasta(seqs[parts == 2], file = here::here("final_library/trimming/all_db.fasta"),
                    line_length = 80, block_length=Inf, append=TRUE)
bioseq::write_fasta(seqs[parts == 3], file = here::here("final_library/trimming/all_db.fasta"),
                    line_length = 80, block_length=Inf, append=TRUE)
bioseq::write_fasta(seqs[parts == 4], file = here::here("final_library/trimming/all_db.fasta"),
                    line_length = 80, block_length=Inf, append=TRUE)
```

# set paths to qiime with cutadapt for trimming

```{r}
# Append qiime2 path to PATH
current_path_env <- Sys.getenv("PATH")

# Also set qiime2 conda environment in batchtools.slurm.tmpl
Sys.setenv(PATH=paste0("/mnt/galaxy/home/mecarew/.local/bin:",
                       current_path_env))
Sys.setenv(PYTHONPATH="/mnt/galaxy/home/mecarew/miniconda2/bin")
```

# check cutadapt has been found (no errors reported) LOOK in terminal (not console)
```{bash}
# Print which cutadapt is being run (it should be the one in the conda virtual environment) 
which cutadapt

# Print cutadapt version
cutadapt --version
```

#Step 3: use Cutadapt (python) to create amplicon specific DNA barcode reference libraries.
If working on the ARC macroinvertebrate project the libraries will only need to be set up for the "short" and the "right" amplicon. 

## optimising trimming scripts for 'short' amplicon

# 1. first 'strict' trim (short amplicon)
```{r}
ampliconGroup <- "short"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt1.log")

# Create the trimming directory if it doesn't exist
if (!dir.exists(trimming_dir)) {
  dir.create(trimming_dir, recursive = TRUE)
}

# Construct and execute the Cutadapt command
command <- paste(
    "cutadapt -g TAGGWACWGGWTGAACWGTWTAYCCYCC...CCNGTNYTNGCNGGNGCNATYACGG -e 0.28 --revcomp -m 100 -M 658 --max-n 0.05 ",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short1.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long1.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed1.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/all_db.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

# 2. relaxed trim of '--too long' sequences (short amplicon)
```{r}
# Construct and execute the Cutadapt command
ampliconGroup <- "short"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt2.log")

command <- paste(
    "cutadapt -g WGGWTGAACWGTWTAYCCYCC...YTNGCNGGNGCNATYACGG -e 0.3 --revcomp -m 100 -M 658 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short2.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long2.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed2.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed2.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_too_long1.fasta"),
    ">", log_file,
    collapse = " "
)

#cutadapt -g ACWGGWTGRACWGTNTAYCC...GCHGGDGCHATYACHATRYT -e 0.19 --revcomp -m 100 -M 450 --max-n 0.05"

system(command)
```

# 3. relaxed trim of '--untrimmed' sequences (short amplicon)
```{r}
# Construct and execute the Cutadapt command

ampliconGroup <- "short"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt3.log")

command <- paste(
    "cutadapt -g ACWGGWTGRACWGTNTAYCC...CCNGTNYTNGCNGGNGCNATYACGG -e 0.3 --revcomp -m 100 -M 450 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short3.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long3.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed3.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed3.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_untrimmed1.fasta"),
    ">", log_file,
    collapse = " "
)


system(command)
```

# 4. join trimmed files (short amplicon)
```{r}
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"

# List of trimmed files to concatenate
trimmed_files <- c(
    paste0(output_dir, "/trimming/short_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/short_amplicon_trimmed2.fasta"),
    paste0(output_dir, "/trimming/short_amplicon_trimmed3.fasta"),
    paste0(output_dir, "/trimming/short_amplicon_untrimmed3.fasta")
)

# Output file to create
output_file <- paste0(output_dir, "/short_amplicon_trimmed.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each trimmed file and write its contents to the output file
for (file_path in trimmed_files) {
    # Open current trimmed file
    input_connection <- file(file_path, "r")
    
    # Read contents of current trimmed file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)

```

# right amplicon

# 1. first 'strict' trim (right amplicon)
```{r}
ampliconGroup <- "right"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt1.log")

# Create the trimming directory if it doesn't exist
if (!dir.exists(trimming_dir)) {
  dir.create(trimming_dir, recursive = TRUE)
}

# Construct and execute the Cutadapt command
command <- paste(
"cutadapt -g TAGGWACWGGWTGAACWGTWTAYCCYCC...TGRTTYTTTGGWCAYCCWGAAGTTTA -e 0.25 --revcomp -m 200 -M 658 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short1.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long1.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed1.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/all_db.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#2. relaxed trim of '--too long' sequences (right amplicon)
```{r}
# Construct and execute the Cutadapt command
ampliconGroup <- "right"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt2.log")

command <- paste(
    "cutadapt -g WACWGGWTGAACWGTWTAYCCYCC...GCHGGDGCHATYACHATRYT -e 0.1 --revcomp -m 200 -M 658 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short2.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long2.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed2.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed2.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_too_long1.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#3. relaxed trim of '--untrimmed' sequences (right amplicon)
```{r}
# Construct and execute the Cutadapt command

ampliconGroup <- "right"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt3.log")

command <- paste(
    "cutadapt -g WGGWTGAACWGTWTAYCCYC...GCHGGDGCHATYACHATRYT -e 0.14 --revcomp -m 100 -M 658 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short3.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long3.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed3.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed3.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_untrimmed1.fasta"),
    ">", log_file,
    collapse = " "
)


system(command)
```

```{r}
# Construct and execute the Cutadapt command

ampliconGroup <- "right"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt3.log")

command <- paste(
    "cutadapt -g ACWGGWTGRACWGTNTAYCC...GRTTYTTYGGNCAYCCHGA -e 0.26 --revcomp -m 100 -M 658 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short4.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long4.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed4.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed4.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_untrimmed3.fasta"),
    ">", log_file,
    collapse = " "
)


system(command)
```

#4.join trimmed files (right amplicon)
```{r}
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"

# List of trimmed files to concatenate
trimmed_files <- c(
    paste0(output_dir, "/trimming/right_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/right_amplicon_trimmed2.fasta"),
    paste0(output_dir, "/trimming/right_amplicon_trimmed3.fasta"),
    paste0(output_dir, "/trimming/right_amplicon_trimmed4.fasta"),
    paste0(output_dir, "/trimming/right_amplicon_untrimmed4.fasta")
)

# Output file to create
output_file <- paste0(output_dir, "/right_amplicon_trimmed.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each trimmed file and write its contents to the output file
for (file_path in trimmed_files) {
    # Open current trimmed file
    input_connection <- file(file_path, "r")
    
    # Read contents of current trimmed file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)

```
#long amplicon

# 1. first 'strict' trim (long amplicon)
```{r}
ampliconGroup <- "long"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt1.log")

# Create the trimming directory if it doesn't exist
if (!dir.exists(trimming_dir)) {
  dir.create(trimming_dir, recursive = TRUE)
}

# Construct and execute the Cutadapt command
command <- paste(
"cutadapt -g ACWGGWTGRACWGTNTAYCC...TGRTTYTTYGGNCAYCCHGA -e 0.3 --revcomp -m 200 -M 550 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short1.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long1.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed1.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/all_db.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#2. relaxed trim of '--too long' sequences (long amplicon)
```{r}
# Construct and execute the Cutadapt command
ampliconGroup <- "long"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt2.log")

command <- paste(
    "cutadapt -g GCHCCHGAYATRGCHTTYCC...TGRTTYTTYGGNCAYCCHGA -e 0.32 --revcomp -m 200 -M 550 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short2.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long2.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed2.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed2.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_too_long1.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#3. relaxed trim of '--untrimmed' sequences (long amplicon)
```{r}
# Construct and execute the Cutadapt command

ampliconGroup <- "long"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt3.log")

command <- paste(
    "cutadapt -g GCHCCHGAYATRGCHTTYCC...TGRTTYTTYGGNCAYCCHGA -e 0.35 --revcomp -m 200 -M 550 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short3.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long3.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed3.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed3.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_untrimmed1.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#4.join trimmed files (long amplicon)
```{r}
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"

# List of trimmed files to concatenate
trimmed_files <- c(
    paste0(output_dir, "/trimming/long_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/long_amplicon_trimmed2.fasta"),
    paste0(output_dir, "/trimming/long_amplicon_trimmed3.fasta")
)

# Output file to create
output_file <- paste0(output_dir, "/long_amplicon_trimmed.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each trimmed file and write its contents to the output file
for (file_path in trimmed_files) {
    # Open current trimmed file
    input_connection <- file(file_path, "r")
    
    # Read contents of current trimmed file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)

```

   
#left amplicon 

# 1. first 'strict' trim (left amplicon)
```{r}
ampliconGroup <- "left"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt1.log")

# Create the trimming directory if it doesn't exist
if (!dir.exists(trimming_dir)) {
  dir.create(trimming_dir, recursive = TRUE)
}

# Construct and execute the Cutadapt command
command <- paste(
"cutadapt -g CCNGAYATRGCNTTYCC...CCNGTNYTNGCNGGNGCNATYACH -e 0.2 --revcomp -m 200 -M 450 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short1.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long1.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed1.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/all_db.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#2. relaxed trim of '--too long' sequences (left amplicon)
```{r}
# Construct and execute the Cutadapt command
ampliconGroup <- "left"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt2.log")

command <- paste(
    "cutadapt -g CCNGAYATRGCNTTYCC...CCNGTNYTNGCNGGNGCNATYACH -e 0.37 --revcomp -m 200 -M 450 --max-n 0.05 ",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short2.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long2.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed2.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed2.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_too_long1.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#3. relaxed trim of '--untrimmed' sequences (left amplicon)
```{r}
# Construct and execute the Cutadapt command

ampliconGroup <- "left"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt3.log")

command <- paste(
    "cutadapt -g CCNGAYATRGCNTTYCC...CCNGTNYTNGCNGGNGCNATYACH -e 0.37 --revcomp -m 200 -M 450 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short3.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long3.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed3.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed3.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_untrimmed1.fasta"),
    ">", log_file,
    collapse = " "
)


system(command)
```

#4.join trimmed files (left amplicon)
```{r}
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"

# List of trimmed files to concatenate
trimmed_files <- c(
    paste0(output_dir, "/trimming/left_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/left_amplicon_trimmed2.fasta"),
    paste0(output_dir, "/trimming/left_amplicon_trimmed3.fasta")
)

# Output file to create
output_file <- paste0(output_dir, "/left_amplicon_trimmed.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each trimmed file and write its contents to the output file
for (file_path in trimmed_files) {
    # Open current trimmed file
    input_connection <- file(file_path, "r")
    
    # Read contents of current trimmed file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)
```


# LCO amplicon 

# 1. first 'strict' trim (LCO amplicon)
```{r}
ampliconGroup <- "lco"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt1.log")

# Create the trimming directory if it doesn't exist
if (!dir.exists(trimming_dir)) {
  dir.create(trimming_dir, recursive = TRUE)
}

# Construct and execute the Cutadapt command
command <- paste(
"cutadapt -g ATCATAAAGAYATYGG...DGCHATYACHATRYT -e 0.2 --revcomp -m 200 -M 550 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short1.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long1.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed1.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/all_db.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```


#2. relaxed trim of '--too long' sequences (lco amplicon)
```{r}
# Construct and execute the Cutadapt command
ampliconGroup <- "lco"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt2.log")

command <- paste(
    "cutadapt -g ATCATAAAGAYATYGG...DGCHATYACHATRYT -e 0.4 --revcomp -m 200 -M 550 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short2.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long2.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed2.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed2.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_too_long1.fasta"),
    ">", log_file,
    collapse = " "
)

system(command)
```

#3. relaxed trim of '--untrimmed' sequences (lco amplicon)
```{r}
# Construct and execute the Cutadapt command

ampliconGroup <- "left"
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"
trimming_dir <- paste0(output_dir, "/trimming/")
log_file <- paste0(trimming_dir, ampliconGroup, "_amplicon_cutadapt3.log")

command <- paste(
    "cutadapt -g ATCATAAAGAYATYGG...DGCHATYACHATRYT -e 0.4 --revcomp -m 200 -M 550 --max-n 0.05",
    "--too-short-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_short3.fasta"),
    "--too-long-output", paste0(trimming_dir, ampliconGroup, "_amplicon_too_long3.fasta"),
    "--untrimmed-output", paste0(trimming_dir, ampliconGroup, "_amplicon_untrimmed3.fasta"),
    "-o", paste0(trimming_dir, ampliconGroup, "_amplicon_trimmed3.fasta"),
    paste0(trimming_dir, ampliconGroup,"_amplicon_untrimmed1.fasta"),
    ">", log_file,
    collapse = " "
)


system(command)
```

#4.join trimmed files (lco amplicon)
```{r}
output_dir <- "/mnt/galaxy/home/mecarew/git/DNA_barcode_reference_database_construction/final_library"

# List of trimmed files to concatenate
trimmed_files <- c(
    paste0(output_dir, "/trimming/lco_amplicon_trimmed1.fasta"),
    paste0(output_dir, "/trimming/lco_amplicon_trimmed2.fasta"),
    paste0(output_dir, "/trimming/lco_amplicon_trimmed3.fasta")
)

# Output file to create
output_file <- paste0(output_dir, "/left_amplicon_trimmed.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each trimmed file and write its contents to the output file
for (file_path in trimmed_files) {
    # Open current trimmed file
    input_connection <- file(file_path, "r")
    
    # Read contents of current trimmed file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)
```

#Step 4: Merge sequences back together with taxonomic information.

# Set parameters for writing files into library file format for the bioinformatic pipeline. 
The output flies will include a text file containing the taxonomic information ant a fasta file with the sequence data.
```{r}
# Write files
# Change from default behaviour (refdb::refdb_export_mothur and bioseq::write_fasta)
# - include taxonomy labels, e.g. k__Eukaryota;p__Arthropoda;c__Insecta
# - only use taxonmy levels: k, p, c, o, f, g, s
# - single line break between sequences and no block size
# Also add n_parts argument to split writing fasta file in multiple parts to avoid memory issues

write_db_files <- function (x, path_prefix, n_parts) {
    # Which taxonomy levels to include in output and the label names:
    tax_levels <- c("k" ="superkingdom", "p"="phylum", "c"="class", "o"="order", "f"="family",
                    "g"="genus", "s"="species")
    refdb:::check_fields(x, what = c("sequence", "taxonomy", "id"))
    # col_tax <- attributes(x)$refdb_fields$taxonomy
    col_tax <- tax_levels
    col_id <- attributes(x)$refdb_fields$id
    col_seq <- attributes(x)$refdb_fields$sequence
    labs <- x[[col_id]]
    labs <- stringr::str_replace_all(labs, "[:blank:]", "_")
    seqs <- x[[col_seq]]
    names(seqs) <- labs
    # Change NA values to ""
    x[, col_tax][is.na(x[, col_tax])] <- ""
    # Add labels names
    tax <- apply(x[, col_tax], 1, function(x) paste0(names(tax_levels), "__", x, collapse = ";"))
    tax <- paste0(labs, "\t", tax, ";")
    file_fas <- paste0(path_prefix, ".fasta")
    file_txt <- paste0(path_prefix, ".txt")
    if (n_parts <= 1) {
      write_fasta(seqs, file = file_fas)
    } else {
      write_fasta_parts(seqs, file = file_fas, n_parts=n_parts)
    }
    
    readr::write_lines(tax, file = file_txt)
}

write_fasta_parts <- function(x, file, n_parts) {
  parts <- as.numeric(cut(seq_along(x), n_parts))
  for (i in 1:n_parts) {
    if (i == 1) {
      write_fasta(x[parts == i], file = file,
                  line_length = 80, block_length=Inf, append=FALSE)
    } else {
      write_fasta(x[parts == i], file = file,
                  line_length = 80, block_length=Inf, append=TRUE)
    }
  }
}

write_fasta <- function (x, file, append = FALSE, line_length = 80, block_length = Inf) 
{
    x_nchar <- stringr::str_length(x)
    x_is_na <- is.na(x)
    if (line_length == Inf) {
        line_length <- max(x_nchar, na.rm = TRUE)
    }
    if (block_length == Inf) {
        block_length <- line_length
    }
    blocks_by_line <- line_length/block_length
    if (block_length > line_length) {
        stop("The length of blocks cannot be higher than the length of lines")
    }
    if (line_length%%block_length > 0L) {
        stop("The length of lines must be a multiple of the length of blocks")
    }
    if (any(x_is_na | x_nchar == 0L)) {
        input_len <- length(x)
        x <- x[!is.na(x)]
        output_len <- length(x)
        warning("Found ", input_len - output_len, " NA and/or empty sequences. They were not exported since ", 
            "the FASTA format does not support missing values.")
    }
    x <- as.character(x)
    x <- vapply(x, function(x) {
        x_len <- stringr::str_length(x)
        blocks <- seq(1, x_len, by = block_length)
        res <- stringr::str_sub(x, blocks, blocks - 1 + block_length)
        separator <- rep(" ", length(res))
        if (x_len > line_length) {
            separator[seq(blocks_by_line, blocks_by_line * (x_len%/%line_length), 
                blocks_by_line)] <- "\n"
        }
        separator[length(separator)] <- ""
        res <- stringr::str_c(res, separator, collapse = "")
        res
    }, vector("character", 1))
    fas <- stringr::str_c(">", names(x), sep = "")
    fas <- stringr::str_c(fas, x, sep = "\n", collapse = "\n") # Changed collapse to one line break
    readr::write_file(fas, file, append = append)
    readr::write_file("\n", file, append = TRUE) # Add one additional line break at the end
}
```

# Write all - set directories
```{r}
# Output prefix name and input file path
db_files <- c(
  "short_db_2023-07_1" = "~/git/DNA_barcode_reference_database_construction/final_library/short_amplicon_trimmed.fasta",
  "right_db_2023-07_1" = "~/git/DNA_barcode_reference_database_construction/final_library/right_amplicon_trimmed.fasta",
"long_db_2023-07_1" = "~/git/DNA_barcode_reference_database_construction/final_library/long_amplicon_trimmed.fasta",
 "left_db_2023-07_1" = "~/git/DNA_barcode_reference_database_construction/final_library/left_amplicon_trimmed.fasta",
"lco_db_2023-07_1" = "~/git/DNA_barcode_reference_database_construction/final_library/right_amplicon_trimmed.fasta")
```

# Write all - write data as .txt files for taxonomic information and .fasta files with the sequence data
```{r}
output_dir <- "~/git/DNA_barcode_reference_database_construction/final_library"
for (i in seq_along(db_files)) {
  message("Processing ", names(db_files[i]))
  fasta <- bioseq::read_fasta(file=db_files[i])
  db <- all_db[str_remove(names(fasta), " rc$"),]
  db$sequence <- fasta
  db <- db %>% filter(! is.na(id))
  message("Writing files for ", names(db_files[i]))
  write_db_files(db, path_prefix=file.path(output_dir, names(db_files[i])), n_parts = 10)
}
```


# Add in important species inadvertantly omitted from amplicon libraries can be added at this point to produce final libraries

# right amplicon (combine fasta files)
```{r}
# List of files to concatenate
final_lib <- c(
    paste0(output_dir, "/right_db_2023-07_1.fasta"),
    paste0(output_dir, "/amp_mis_sp/right_miss.fasta")
) 

# Output file to create
output_file <- paste0(output_dir, "/right_db_2023-07.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each file and write its contents to the output file
for (file_path in final_lib) {
    # Open current file
    input_connection <- file(file_path, "r")
    
    # Read contents of current file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)
```

# right amplicon (text files)
```{r}
# File paths
amp_lib <- here::here("final_library/right_db_2023-07_1.txt")
mis_sp <- here::here("final_library/amp_mis_sp/right_miss.txt")
output_file <- here::here("final_library/right_db_2023-07.txt")

# Read contents of file1
amp_lib_tax <- readLines(amp_lib)

# Read contents of file2
mis_sp_tax <- readLines(mis_sp)

# Combine contents of both files
fin_lib_tax <- c(amp_lib_tax, mis_sp_tax)

# Write combined content to a new file
writeLines(fin_lib_tax, output_file)
```

# short amplicon (combine fasta files)
```{r}
# List of files to concatenate
final_lib <- c(
    paste0(output_dir, "/short_db_2023-07_1.fasta"),
    paste0(output_dir, "/amp_mis_sp/short_miss.fasta")
) 

# Output file to create
output_file <- paste0(output_dir, "/short_db_2023-07.fasta")

# Open output file in write mode
output_connection <- file(output_file, "w")

# Loop through each file and write its contents to the output file
for (file_path in final_lib) {
    # Open current file
    input_connection <- file(file_path, "r")
    
    # Read contents of current file
    file_contents <- readLines(input_connection)
    
    # Write contents to output file
    writeLines(file_contents, output_connection)
    
    # Close input file connection
    close(input_connection)
}

# Close output file connection
close(output_connection)
```

# short amplicon (text files)
```{r}
# File paths
amp_lib <- here::here("final_library/short_db_2023-07_1.txt")
mis_sp <- here::here("final_library/amp_mis_sp/short_miss.txt")
output_file <- here::here("final_library/short_db_2023-07.txt")

# Read contents of file1
amp_lib_tax <- readLines(amp_lib)

# Read contents of file2
mis_sp_tax <- readLines(mis_sp)

# Combine contents of both files
fin_lib_tax <- c(amp_lib_tax, mis_sp_tax)

# Write combined content to a new file
writeLines(fin_lib_tax, output_file)
```