---
title: "Private_database_checks_corrections"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

This step imports DNA barcodes which I have produced from invertebrates. It is a mixture of unpublished and published data. The private reference library is managed in Geneious prime.

#read in DNA barcode datafile in .csv 
```{r}
priv_lib <- read_csv ("~/Documents/DNA_reference_db_construction/refdb/Input_data_Oct23/priv_lib_oct23.csv")
```

# Corrections to private library
Chris- I have included the scripts below in this R markdown for now so I could complete the libraries. I would like to have the scripts you put together for check the data against BOLD with any other corrections needed and in a separate R markdown (or Qmd). The idea being that the corrected and vetted data can then be imported into this document for constructing the final libraries.
```{r}
priv_lib$species <- gsub("Craspedacusta sowerbyi", "Craspedacusta sowerbii",
                         gsub("Polypedilum griseguttataum", "Polypedilum griseoguttatum",
                              gsub("Culicoides bundyensi", "Culicoides bundyensis",
                                   gsub("Austrophlebiodies pusillus", "Austrophlebioides pusillus",
                                        gsub("AustroLimnophila", "Austrolimnophila",
                                             gsub("Paralimnophila sp. B-private", "Paralimnophila sp. B-ACM3182",
                                                  gsub("Ferrissia sp. B-AAY1880", "Ferrissia sp. B-ADR3570",
                                                    gsub("\\'", "", priv_lib$species))))))))
priv_lib$family <- gsub("Chironominae",
                        "Chironomidae", priv_lib$family)
priv_lib$order <- gsub("Unionoida",
                       "Unionida", priv_lib$order)
priv_lib$genus <- gsub("AustroLimnophila", "Austrolimnophila", priv_lib$genus)


#check corrections have been made

Praon volucre
print (sum(str_detect(priv_lib$species, 'Craspedacusta sowerbii')) > 0)
print (sum(str_detect(priv_lib$species, 'Polypedilum griseoguttatum')) > 0)
print (sum(str_detect(priv_lib$species, 'Culicoides bundyensis')) > 0)
print (sum(str_detect(priv_lib$species, 'Austrophlebioides pusillus')) > 0)
#should be TRUE
print (sum(str_detect(priv_lib$family, 'Chironominae')) > 0)
#should be NA
print (sum(str_detect(priv_lib$order, 'Unionoida')) > 0)
#should be NA

#records for updating (theses temporary scripts for now corrections so the amplicon library could be completed)
#629 VIS3TLN50 Ceratopogonidae sp. B-AAV5109 Ceratopogonidae sp. B-AED5657
priv_lib[629,6] <- "Ceratopogonidae sp. B-AED5657"

#831 BCM32T1Tany1 Ablabesmyia sp. B-AEN4439 Ablabesmyia sp. B-AEN4438
priv_lib[831,6] <- "Ablabesmyia sp. B-AEN4438"

#990 IS04CL15 Cladopelma sp. B-AAE2753 IS04CL15 Cladopelma sp. B-AAE2754
priv_lib[990,6] <- "Cladopelma sp. B-AAE2754"

#991 IS04CL16 Cladopelma sp. B-AAE2753 IS04CL15 Cladopelma sp. B-AAE2754
priv_lib[991,6] <- "Cladopelma sp. B-AAE2754"

#1140 A03Cy31 Cryptochironomus sp. B-ACS4478 Cryptochironomus sp. B-ACS3865
priv_lib[1140,6] <- "Cryptochironomus sp. B-ACS5094"

#1141 A03Cy37 Cryptochironomus sp. B-ACS4478 Cryptochironomus sp. B-ACS5094
priv_lib[1141,6] <- "Cryptochironomus sp. B-ACS5094"

#1214 Larsia sp. B-AAV5971 Larsia sp. B-AEH6175
priv_lib[1214,6] <- "Larsia sp. B-AEH6175"

#1215 A03A7 Larsia sp. B-AAV5971 Larsia sp. B-AEN3053
priv_lib[1215,6] <- "Larsia sp. B-AEN3053"

#1216 BOL97Tany1 Larsia sp. B-AAV5971 Larsia sp. B-AEH6175
priv_lib[1216,6] <- "Larsia sp. B-AEH6175"

#1217 A03A7 Larsia sp. B-AAV5971 Larsia sp. B-AEN3053
priv_lib[1217,6] <- "Larsia sp. B-AEN3053"

#1218 E06T60  Larsia sp. B-AAV5971 Larsia sp. B-AEH6175
priv_lib[1218,6] <- "Larsia sp. B-AEH6175"

#1220 E06Tp7 Larsia sp. B-AAV5971 Larsia sp. B-AEN3053
priv_lib[1220,6] <- "Larsia sp. B-AEN3053"

#1249 BR08C4 Parachironomus sp. B-ACQ1891 Parachironomus sp. B-ACQ1891
priv_lib[1249,6] <- "Parachironomus sp. B-ACQ1891"

#1356 E06Po119 Polypedilum sp. B-ACQ1510 Polypedilum sp. B-ACQ1511
priv_lib[1356,6] <- "Polypedilum sp. B-ACQ1511"

#1358 E06Po74 Polypedilum sp. B-ACQ1510 Polypedilum sp. B-ACQ1511
priv_lib[1358,6] <- "Polypedilum sp. B-ACQ1511"

#1360 MC09C3 Polypedilum sp. B-ACQ1510 Polypedilum sp. B-ACQ1511
priv_lib[1360,6] <- "Polypedilum sp. B-ACQ1511"

#1361 Polypedilum sp. B-ACQ1510 Polypedilum sp. B-ACQ1511
priv_lib[1361,6] <- "Polypedilum sp. B-ACQ1511"

#2426 Co18Cono6 Lingora sp. B-AAY5550 Lingora sp. B-ADF2103
priv_lib[1141,6] <- "Lingora sp. B-ADF2103"
```
# add superkingdom column to bring in line with NCBI GenBank data
```{r}
priv_lib <- priv_lib %>%
mutate(superkingdom = "Eukaryota",
  .before = "phylum")
```

# set fields for refdb
```{r}
priv_lib <- refdb::refdb_set_fields(priv_lib,
                             taxonomy = c(kingdom ="superkingdom",
                               phylum = "phylum",
                               class = "class",
                               order = "order",
                               family = "family",
                               genus = "genus",
                               species = "species"),
                             sequence = "DNA_seq",
                             marker = "marker",
                             source = "source",
                             id = "id")

refdb::refdb_get_fields(priv_lib)
```
#Step 1: Remove duplicates.
```{r}
priv_lib_clean <- refdb::refdb_filter_seq_duplicates(priv_lib)

rm(priv_lib)
```

# plot sequence length
```{r}
refdb::refdb_plot_seqlen_hist(priv_lib_clean)
```

Note: Primer cropping in refdb does not work! I could not get refdb to properly trim primers it needed really high error setting to do any trimming, but with these settings over trimmed most of the data. for the short amplicon the forward primer trims ok but the reverse trims in the wrong spot.

#Visualizing the reference library (Optional)

Now let’s take a tour of the functions you can use to produce graphical representation of your reference database. Because refdb stores reference database as dataframes it is straightforward to produce plots (e.g. with the tidyverse and ggplot2). For example, we can make a barplot showing the distribution of the families like this:
  
```{r}
priv_lib_clean %>% 
  group_by(phylum) %>% 
  count() %>% 
  ggplot(aes(fct_reorder(phylum, n, .desc = TRUE), n)) +
  geom_col() +
  xlab("Phylum") +
  ylab("Number of records") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

```{r}
priv_lib_clean %>% 
  group_by(class) %>% 
  count() %>% 
  ggplot(aes(fct_reorder(class, n, .desc = TRUE), n)) +
  geom_col() +
  xlab("Class") +
  ylab("Number of records") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
```

Additionally, refdb provides ready-to-use functions to produce more sophisticated plots. For example, to represent the taxonomic coverage of your reference library across multiple levels with a tree map:
  
Jess - This does not work but not important as there is simply too much data to get anything meaningful out.

```{r}
refdb::refdb_plot_tax_treemap(priv_lib_clean, cols = 4)
```

Alternatively you can represent this information with a taxonomic tree. These functions have several parameters to control what is represented in the plot (taxonomic ranks, colors, etc.).

```{r}
refdb_plot_tax_tree(priv_lib_clean)
```

# Creating a report
A report is a simple and rapid way to get an overview of the current state of your reference library and to identify some possible issues. You can compile a report using the function refdb_report: 
  
```{r}
refdb::refdb_report(priv_lib_clean, view=TRUE)
```                    

# Exporting cleaned private data
Once satisfied with the results, they can be exported for further use. Since the reference database is a dataframe, it is possible to use any export functions (from R or from other packages) that support dataframes. Here we show how to export to CSV using the function write_csv from the readr package:

```{r}
write_rds(priv_lib_clean, "~/Documents/DNA_reference_db_construction/refdb/Output_data_Oct23/priv_lib_Oct23_clean.rds")
```

# importing (if required)

```{r}
priv_lib_clean <- readRDS("~/Documents/DNA_reference_db_construction/refdb/Output_data_Oct23/priv_lib_Oct23_clean.rds")
```

# set fields for priv_lib_clean
```{r}
priv_lib_clean <- refdb_set_fields(priv_lib_clean,
                             taxonomy = c(
                               phylum = "phylum",
                               class = "class",
                               order = "order",
                               family = "family",
                               genus = "genus",
                               species = "species"),
                             sequence = "DNA_seq",
                             marker = "marker",
                             source = "source",
                             id = "id")

refdb_get_fields(priv_lib_clean)
```

